---
title: "Stats380 exam"
author: "Kerui Du"
date: "04/11/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Q1

###(a)
```{r 1a}
(1:10)^(1:2)
```

###(b)
```{r 1b}
seq(1,19,by=3)
```

###(c)
```{r 1c}
(1:18)[-seq(2,17,by=3)]

```

###(d)
```{r 1d}
rep(1:9,rep(3:1,3))
```

###(e)
```{r 1e}
1:16 %/% 5 
```


## Q2

(a)

X[X>=-1 & X<=1]

(b)

X[X<mean(X,na.rm=T)]

(c)

X[3:length(X)-2]


## Q3

###(a)
```{r 3a}
# funQ3a = function{
#   max_n = apply(matrix(1:9,3),2,max)
#   min_n = apply(matrix(1:9,3),2,min)
#   return((a+b)/2)
# }
```



## Q4
```{r}
 mat = matrix(c(0, 0, 0, 0, 0,
                0, 6, 6, 6, 0,
                0, 4, 0, 5, 0,
                0, 1, 2, 2, 0,
                0, 0, 3, 0, 0,
                0, 7, 7, 7, 0,
                0, 0, 0, 0, 0), nc=5, byrow=T);
layout(mat,widths = c(lcm(1), 1, lcm(2.5), 1, lcm(1)), 
       heights = c(lcm(1), lcm(1.5), lcm(1.5), 1, lcm(2), lcm(1),lcm(1)))
layout.show(7)
box('o', lty= 'solid', col='red', lwd = 2)
```

## Q5
```{r}
# plot(dat$flush.dist, cex = 0.75, xlim = c(0, 650), ylim = c(0, 200), 
#      xlab = 'Individuals', ylab = 'Distance (m)', type= 'b', col='blue')
# points(dat$flush.dist, cex = 0.75, pch = 16, col = 'red')
# lines(dat$flush.dist, cex = 0.75, pch =16, col = 'red')
# legend('topright', c('Flushing distance', 'Landing distance'),lty = c(1,1), 
#        pch = c(1, 16), col = c('blue','red'), bty = 'n',cex = 0.75)
# text(x = 170, y = 200, labels = 'Oystercatchers')
# lines(x = c(-20, 670), y = c(max(dat$flush.dist),max(dat$flush.dist)), lty = 2)
```

## Q6

### (a) grepl("red", text):
###     The grepl function determines whether if the 'red' exist in each element of text, 
###     if it is, return TRUE, otherwise return FALSE


### (b) gsub("<.*?>", "", text):
###     if any element in the text contains the pattern that start from '<' end with '>' and each character replace by ''


### (c) strsplit(text, "[,|.]") 
###     each element in the text split by ',' or '.' 


### (d) regmatches(text, gregexpr("^[0-9]+", text)) = ""
###     find 1 or more length of number from start of each element in the text and these numbers replace by ''. The data structure of text wouldn't chanage


### (e) sapply(strsplit(text, "\\."), length)
###     split each element of text at '\\ and a letter', and count the number of elements after splitting and create a list which contains these counts.



## Q7
```{r}
# HTMLTable <- function(text) {
#   readin = readLines(text)
#   index1 = grep('<table',readin)
#   index2 = grep('/table>',readin)
#   paste(readin[index1:index2],collapse = '')
# }
```

## Q8
```{r}
row1=' <tr><th> Country </th><th> Population </th> <th> Yearly Change </th><th>Density </th> </tr> '
row2=' <td> 2021 </td><td> New Zealand </td> <td> Auckland </td> '
processRow <- function(row) {
  mod1 = strsplit(row,'<th>|<td>')[[1]][-1]
  mod2 = sub(' <.+$','',mod1)
  mod3 = sub('^ ','',mod2)
  mod3
}
processRow(row1)
processRow(row2)
```

## Q9
```{r}
# group.stats <- function(data) {
#   factors = as.factor(data$group)
#   means = aggregate(cbind(x1,x2,x3)~group,mean,data=df)
#   cov = lapply(levels(factors), function(x) cov(subset(data,group==x)[-1])) 
#   list(means=means,cov=cov)
# }

```

## Q10
```{r}
# df = sapply(oceania, readTable.country)
# mod_df = lapply(1:length(oceania), function(i) cbind(Country=oceania[i],df[[i]][1:2]))
# f_df = do.call(rbind,mod_df)

```

## Q11
```{r}
# final_df=(with(f_df,tapply(Population, list(Country,as.factor(Year)), mean)))
# final_df = as.data.frame(final_df)
# final_df=cbind(Country=rownames(final_df),final_df)
# rownames(final_df)=1:nrow(final_df);final_df
```

